---
title: "simpleRegress"
author: "Luz Vargas"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp2 <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp2)
summary.lm(simp2)
```

The adjusted R square for this model is smaller than the model using neck since the neck since the adjusted R-squared for the neck model was 0.7476 and the adjusted R-squared model for Head width was 0.5321.


```{r}
simp3 <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp3)
summary.lm(simp3)
```

The Adjusted R-square for this model is 0.7423 which is still smalled than the neck model which is 0.7476.


```{r}
simp4 <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp4)
summary.lm(simp4)
```

The adjusted R-square for the chest model is 0.7869 which is bigger than the adjusted R-square for the neck which is 0.7476.


```{r}
simp5 <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp5)
summary.lm(simp5)
```

